\centering Syscoin 4：一种点对点的电子现金系统 - 用于去中心化Web3.0商业应用

### 2022-08-05 syscoin_4_mandarin/article_final.tex
mandarin translation

\documentclass[peerreview]{ieeesyscoin}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage[switch]{lineno}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\history{}

\title{\centering Syscoin 4: A Peer-to-Peer Electronic Cash System Built For Decentralized
Web 3.0 Business Applications}
\author{\centering  \uppercase{Jagdeep Sidhu, MSc}\authorrefmark{1}, 
and \uppercase{Ian C. Moore, PhD\authorrefmark{2}}}

\address[1]{\centering Syscoin Core Developer, Blockchain Foundry Inc.(e-mail: jsidhu@blockchainfoundry.co)}
\address[2]{\centering  (Syscoin Researcher, e-mail: imoore@syscoin.org)}
\tfootnote{}

\markboth
{Sidhu \headeretal: Syscoin 4: A Peer-to-Peer Electronic Cash System Built For Decentralized
Web 3.0 Business Applications}
{Sidhu \headeretal: Syscoin 4: A Peer-to-Peer Electronic Cash System Built For Decentralized Web 3.0 Business Applications}

\corresp{}

\begin{abstract}
Syscoin 4 introduces a novel implementation of a UTXO Asset platform with instant, pseudo-interactive, zero-confirmation, double-spend protected cryptocurrency transactions (Z-DAG) as well as an EVM, both secured via Nakamoto Consensus PoW through merged-mining with Bitcoin. Masternodes providing bonded validators with chainlocks help to reduce selfish-mining opportunities as well as provide the network with full node security. The EVM scales on layer 2 with Zero-Knowledge Proofs and the UTXO Asset platform scales on layer 2 with payment channels.
\end{abstract}

\begin{keywords}
Network EVM, DAG, Decentralized Identity, Zero-Knowledge Proofs, UTXO, Assets, Layer 2, Web3
\end{keywords}

\titlepgskip=-15pt

@@

\section{Introduction}
\label{sec:introduction}

Syscoin 4 builds on Syscoin 3 with the additional implementation of an Ethereum Bridge, Offers/Escrow, Lightning Network, and Decentralized Identity. As previously featured \cite{Sida18}, anything pertaining to the Marketplace (e.g., digital sales, auctions, marketplace modification, etc.) has been deprecated. The full release will include the Syscoin Network-Enhanced Virtual Machine (NEVM), which will utilize the Ethereum Virtual Machine (EVM) coupled with a Zero-Knowledge Proof (ZKP) system to build scalable applications, and the introduction of a decentralized cost model around Ethereum Gas fees (see Table \ref{table:ugrades}).

High gas fees and low transaction throughput are some of the key issues that are hindering ERC-20 projects from running at scale. Ethereum 2.0 is currently under development to address these issues. However, its final release is not anticipated to be completed for several years \cite{But19}. Instead of building a competing smart contract system, we have decided to work with the EVM protocol to build a faster, cost effective, alternative to Ethereum 2.0. To achieve this, the roadmap for Syscoin 4 proposes a four-layer tech-stack \cite{Sig21} comprised of: (a) Syscoin as the base layer to provide security; (b) EVM for programmability; (c) ZKP for scalability; and (d) applications to provide decentralized usability for the next phase of the internet's evolution, known as Web 3.0.

In Section \ref{sec:protocol} we address the protocol attributes, which include Z-DAG, order-of-events, point-of-sale applications, assets, non-fungible tokens, Lightning Networks, offers/escrow, and masternodes. In Section \ref{section:roadmap} we lay out the roadmap for Syscoin 4, which includes scalability, design proposal, performance evidence, and applications. In Section \ref{section:specs} we outline the protocol specifications, and conclude the article in Section \ref{section:summary}.

\begin{table}[h!]
\caption{Syscoin 4 Upgrades and Modifications}
\label{table:ugrades}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{|p{135pt}|p{75pt}|}
\hline
Syscoin Feature & 
Update \\

\hline
Nakamoto ZDAG (ie, Z-Dag) & no change \\
Assets & modified \\

Offers and decentralized marketplace &   \\
~~~~~ Digital Sales &  deprecated \\
~~~~~ Auctions &  deprecated \\
~~~~~ Reselling w/ whitelists &  deprecated \\
~~~~~ Feedback and rating &  deprecated \\
~~~~~ Multiple payment options &  deprecated \\
~~~~~ Shipping notification system &  deprecated \\
~~~~~ Marketplace moderation &  deprecated \\

Data Anchoring &  deprecated \\
Instant Encrypted Messages &  re-purposed \\
Blockchain pruning &  deprecated \\
Certificates (see Identity) &  modified \\
Decentralized Identity &  new feature \\
~~~~~ Certificates &  modified \\
Lightning networks &  new feature \\
Offers / Escrow &  modified \\
Roadmap to Web 3.0 & \\
~~~~~ Network EVM (NEVM) &  new feature  \\
~~~~~ Zero Knowledge Proofs &  new feature \\
~~~~~ NEVM Applications &  proposed \\

\hline
\multicolumn{2}{p{251pt}}{depreciated  $\rightarrow$ removed from Syscoin 4; modified  $\rightarrow$ repurposed from Syscoin 3; new feature  $\rightarrow$ upgrade from Syscoin 3; no update $\rightarrow$ carry-over from Syscoin 3}\\

@@

\section{Protocol Characteristics}
\label{sec:protocol}

\subsection{Z-DAG}
Zero-Confirmation Directed Acyclic Graph (Z-DAG) is an instant settlement protocol functioning across all Syscoin services. Syscoin services consist of Alias Identities, Certificates, Escrow, Offers and Assets. Each service is controlled via an Alias, in which ownership is proven through a private key that matches each
unique address. Z-DAG organizes transactions based on dependencies to build the state in a deterministic fashion. This helps protect against double-spends where an asset is transferred falsely by creating multiple transactions through multiple nodes within a short time \cite{Sida18}.

\begin{figure}[h!]
\includegraphics[width=3in]{img/current_vs_zdag.png}
\caption{Current Blockchain design vs Z-DAG} 
\label{fig:current_vs_zdag}
\end{figure}

Figure \ref{fig:current_vs_zdag}  shows the difference between a regular blockchain and Syscoin’s Z-DAG implementation. Syscoin now has two consensus layers. The upper layer consists of a Z-DAG graph of transactions are represented in the mempool without a block, providing settlement in real-time. The lower layer provides confirmation and conflict resolution preventing double-spend events through existing Proof-of-Work (PoW) consensus.

When verifying, client nodes will create a graph of transactions topologically arranged via ascendants and descendants organized by the asset UTXO being spent. This is the most efficient approach as a circuit detection is not required; rather, it is inherently assumed as it is added to coin indexes in the memory pool.

Z-DAG is a transactional algorithm and does not affect consensus policy. It is meant to be a double-spend detection and prevention algorithm through the transaction policies of Syscoin Core.

A User Interface (UI) layer will notify the user of conflicts in real-time, allowing the transaction to occur in 3 to 5 seconds (i.e., the amount of time the network takes to notice that 2 double-spend transactions are conflicting with each other). This is possible through Syscoin’s Masternode layer that consists of incentivized full nodes paid an allocation of subsidy every block. Every masternode is connected to 25 or more peers, which facilitates high-throughput relay across the network, averaging one or more network hops to transmit from the sender to the receiver nodes.

To accurately detect double-spends, other implementations such as Phantom \cite{Som18} or Spectre \cite{Som15} must replace the longest chain rule to derive the order of events and attacker sequences in a graph.
These implementations end up in a more complex game theoretical situation that has not  been proven mathematically to be accurate in all cases. Syscoin relies on the thoroughly tested Nakamoto consensus model to arrive at a consensus over time rather than simply relying on a DAG.

\subsection{Order-of-events preservation and Conflict Resolution}
Since assets have been migrated to a UTXO model in Syscoin 4, order-of-events and conflict resolution is as simple as relying on the existing UTXO policy of the Bitcoin memory pool code, which orders individual UTXO dependencies as ascendants and descendants per output. The conflict resolution code for double-spending an output was slightly adjusted from the Bitcoin policy by allowing one double-spend attempt for each output to propagate across the network. This ensures that a double-spend will always be detectable by an observer regardless of order-of-events. This is especially important as nodes on the network have no ability to understand the intent of a transaction and are thus not able to know which one is actually a double-spend attempt. To account for the extra bandwidth requirements of allowing a double-spend to be propagated, the minimum relay fee paid in the transaction is double that of a regular transaction.

\subsection{CAP Theorem}
The CAP theorem \cite{Bre12} states that it is impossible for a distributed data store to simultaneously provide more than two out of the following three guarantees: consistency, availability or partition tolerance. Bitcoin attempts to provide a guarantee that transactions are settled, but is not able to do so according to theory. Z-DAG partially trades consistency for availability. Since it is unlikely that a double-spend or re-organization will change the state of someone’s balance, we do not wait for settlement finality by waiting for blocks to confirm. This drastically increases the usability in point-of-sale applications.

The allowance of instant settlements and increased availability requires paying additional attention to users simply trying to double-spend or send transactions too quickly, which may cause the miner view to change from the general network view. The DAG will order the dependency graph of transactions and process in sequence, allowing for better availability (i.e., client making a request for data gets a response) when it comes to instant state changes. The same CAP constraints as PoW will provide a more responsive money transfer mechanism that may be used as a transaction processor instead of simply a settlement layer.

\subsection{Point-of-sale applications}
The combination of using assets with Z-DAG will allow for point-of-sale applications, providing real-time exchange of cryptocurrency assets/tokens.

\subsection{Assets}
We have created a coloured-coin implementation of a UTXO asset model where the commitment to the specific values of the assets are embedded in OPRETURN data carrying payload. The UTXO itself is part of the transaction to keep compatibility with the Bitcoin transaction format. The consensus to prove validity of an asset transaction is to simply compare the map of inputs (pairing of asset GUID and total value across all inputs) and the map of all outputs (pairing of asset GUID and total value across all outputs), which must be equal (note: there is no fee on assets so equality is sufficient to ensure validity). The coin database storing the unspent outputs adds a value to represent the asset identifier (GUID) for asset outputs.

\subsection{Non-Fungible Tokens}

Non-Fungible Tokens (NFTs) are unique Syscoin-based digital assets.  Some potential use cases include: gaming, digital art, physical assets, and digital collectibles. The advantages of using Syscoin over other platforms include, but is not limited to scalability, divisibility, efficiency, and notary capabilities.

By utilizing the NEVM, Syscoin will offer NFTs running on the application layer of its tech-stack, which will offer a competitive advantage over Ethereum in terms of scalability. Another interesting feature Syscoin will offer is divisibility. A good example of this is land ownership where fractions of such assets can be apportioned between multiple parties. Finally, developers will be able to employ notary capabilities by applying custom rule sets to transactions involving NFTs.

NFT, fractional or otherwise, are implemented in the UTXO asset model and of course can be deployed using the ERC-related specifications on the NEVM model as is the case with Ethereum. Notary capabilities are only implemented for the UTXO asset model. However, with validity proofs we are looking to integrate such features on the NEVM model as well.

\subsection{Decentralized Identity}
Decentralized Identity is the cornerstone for secure information and value exchange between people and devices. Typically current implementations leverage Hyperledger Aries to build Identity solutions following the Web3 RFC spec for Decentralized Identifiers (DID's) \cite{DID}. Through the use of public permission settlement of state, and zero-knowledge-proof based validity proofs to attest identity information (i.e., birth certificate or college diploma), we believe this is an ideal solution, which will not only scale to multiple jurisdictions needing to rely on identities issues by governments, but also allow for applications utilizing  social proof-of-person. Scaling is a challenge not only for privacy chains but also private-permissioned blockchains (the registrations of identities are not aggregated and put onto the ledger on a FIFO basis) There is also the issue that settlement happens not on public infrastructure but private and so is susceptible to attacks, which casts doubts over the claim of immutability. Built on zkRollup infrastructure, identity systems can not only scale, but data can remain private and settlement of state can be done on public infrastructure. We leave specific implementations up to integrators and enterprises looking to build next-generation identity solutions.

\subsubsection{Selfish mining}

Selfish mining is a long standing open problem in the Bitcoin ecosystem \cite{Eya18}. However, with the introduction of masternodes and the ChainLocks service, we have innovated a mechanism design that falls back to Nakamoto consensus. Yet, if a chain lock in a block exists will remove selfish mining attack vectors. To understand the solution it is important to understand the design of Multi-quorum based Chain locks.

\subsubsection{Chain locks}

With a subset of nodes offering sybil resistance through the requirement of bonding 100,000 SYS to become active, along with the deterministic masternode feature added in Syscoin 4.2, we have enabled Chain Locks to prevent selfish mining. Dashcore was the first project to implement this idea \cite{Blo18}, which the industry has since widely accepted as a viable solution \cite{Val19}. Our implementation is a simplified and optimized version of the original. We do not implement Instant Send or Private Send transactions. Due to Syscoin being merged-mined with Bitcoin, we believe our chain coupled with Chain Locks becomes more secure via solving Bitcoin’s most vulnerable attack vector (i.e., selfish mining).

Chain Locks are made part of Long-Living Quorums (LLMQ) which leverage aggregatable Boneh–Lynn–Shacham (BLS) signatures that have the property of being able to combine multiple signers in a Distributed Key Generation (DKG) event to sign on decisions. In this setup, a signature can be signed on a group of parties under threshold constraints without any one of those parties holding the private key associated with that signature. In our case, the signed messages would be a ChainLock Signature (CLSIG) which represent claims on what block hashes represent on the canonical chain \cite{Blo18}. This model suggests a very efficient   threshold signature design was needed to reach consensus across the Masternode layer, decide on chain tips, and lock chains, hence preventing selfish mining attacks. See \cite{Bon18} to understand the qualities of BLS signatures in the context of multi-signature use cases.

Ethereum 2.0 caters to the use of BLS signatures through adding precompile opcodes in the Ethereum Virtual Machine (EVM) for the BLS12-381 curve \cite{Dra18}, which Syscoin has adopted. This curve was first introduced in 2017 by Bowe \cite{Bow17}  to the ZCash protocol. Masternodes on Syscoin have adopted this curve and have a BLS key that is associated with each validator. See \cite{Blo18} for performance comparison to ECDSA (Secp256k1) and a discussion on usefulness in contrast to what Bitcoin and Syscoin natively use for signature verification.

\subsection{Lightning Networks}
By extending on the UTXO asset model we look to integrate layer 1 assets into transactions on layer 2 payment channels such as Lightning Networks \cite{Poon16}. Adding multiple assets to LN requires solving theoretical attack vectors related to American call-options as described in \cite{LN}. Since Syscoin UTXO assets enable the transacting of multiple assets in a single transaction, the integration into Lightning Networks should be fairly intuitive once the problems related to American call-options are solved for.

\subsection{Masternodes}

With 2500+ current, active masternodes running fullnodes, Z-DAG becomes more dependable, as does the propagation of blocks and potential forks. Masternodes are bonded through a loss-less strategy of putting 100,000 syscoin in an output and running full nodes in exchange for block rewards. A seniority model incentivizes masternodes to share long-term growth by paying more for the longer period of service as an additional incentive. Half of the transaction fees are shared between the PoW miners and masternodes to ensure long-term alignment once block subsidy becomes negligible. Coins are not locked at any point, and there is no slashing condition if masternode owners decide to move their coins, the rewards to those masternodes simply stop. Sharing Bitcoin’s compact block design, it consumes very little bandwidth to propagate blocks assuming the memory pool of all these nodes is roughly synchronized \cite{BitCore}. The traffic on the network primarily consists of propagating the missing transactions to validate these blocks. Having a baseline for a large number of full nodes that are paid to be running allows us to create a very secure environment for users. It proposes higher costs to would-be attackers who either have to attempt a 51\% attack on Syscoin (i.e., effectively trying to attack the Bitcoin network), or try to game the mesh network by propagating bad information which is made more difficult by incentivized full nodes. The health of a decentralized network relies on the following; (a) the mining component, or consensus to produce blocks, and (b) the network topology to disseminate information in a timely manner in conditions where adversaries might be lurking. The likelihood of other attacks related to race conditions in networking or consensus code are minimized by following a rigorous, thorough and continuous development process. This includes deterministic builds, Fuzz tests, ASAN/MSAN/TSAN, functional/unit tests, multiple clients and adequate code coverage. Syscoin and Bitcoin protocol code bases are merged daily such that the build/signing/test processes are all identical, allowing us to leverage the massive developer base of Bitcoin.  Code quality is reflective of taking worst-case situations into account.

\section{Roadmap to Web 3.0}
\label{section:roadmap}

Bitcoin was the first to offer a practical solution to the General's Dilemma using Crypto Economic rationale and incentives. Ethereum was the first to abstract the concept of Turing completeness within similar frameworks assumed by Bitcoin. What Syscoin presents is a combination of both Bitcoin and Ethereum with intuitions built on top to achieve a more efficient financial computing platform that leverages coordination to achieve consensus using Crypto Economic rationale and incentives. We propose a four-layer tech stack using Syscoin as the base (host) layer, which provides an efficient (i.e., low gas cost per transaction) platform. Some of the main advantages include scalable, decentralized enabling applications, and the introduction of a decentralized cost model around Ethereum gas fees. This new model proposes state-less parallelized execution and verification models while taking advantage of the security offered by the Bitcoin protocol.

\subsection{Scalability and Security}

>>>>

\documentclass{ctexart}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage{authblk}
\title{\centering Syscoin 4：一种点对点的电子现金系统 - 用于去中心化Web3.0商业应用}

\author[1]{Jagdeep Sidhu, MSc}
\author[2]{和Ian C. Moore, PhD}
\affil[1]{Syscoin核心开发人员, Blockchain Foundry Inc.( 邮箱: jsidhu@blockchainfoundry.co) }
\affil[2]{Syscoin研发人员, 邮箱: imoore@syscoin.org}
\date{}

\begin{document}

@@

\begin{abstract}
Syscoin 4 introduces a novel implementation of a UTXO Asset platform with instant, pseudo-interactive, zero-confirmation, double-spend protected cryptocurrency transactions (Z-DAG) as well as an EVM, both secured via Nakamoto Consensus PoW through merged-mining with Bitcoin. Masternodes providing bonded validators with chainlocks help to reduce selfish-mining opportunities as well as provide the network with full node security. The EVM scales on layer 2 with Zero-Knowledge Proofs and the UTXO Asset platform scales on layer 2 with payment channels. 摘要- Syscoin 4 提出了一种新型UTXO 资产平台，用以实现具有即时、伪交互、零确认、双重支出保护的加密货币交易 (Z-DAG) 以及EVM（以太坊虚拟机），两者均借助于与比特币联合挖矿，由Nakamoto 共识PoW（工作量证明）进行保护。Masternodes提供绑定验证器，带有链锁，有助于减少自私挖矿，并为网络提供完整的节点安全性。 EVM 使用零知识证明在第2层扩展，UTXO 资产平台使用支付渠道在第2层扩展。

\end{abstract}

\section{INTRODUCTION 简介}

Syscoin 4 builds on Syscoin 3 with the additional implementation of an Ethereum Bridge, Offers/Escrow, Lightning Network, and Decentralized Identity. As previously featured \cite{Sida18}, anything pertaining to the Marketplace (e.g., digital sales, auctions, marketplace modification, etc.) has been deprecated. The full release will include the Syscoin Network-Enhanced Virtual Machine (NEVM), which will utilize the Ethereum Virtual Machine (EVM) coupled with a Zero-Knowledge Proof (ZKP) system to build scalable applications, and the introduction of a decentralized cost model around Ethereum Gas fees (see Table \ref{table:ugrades}).Syscoin 4以Syscoin 3为基础，额外增加以下内容：以太坊跨链桥、商品/托管、闪电网络和去中心化身份。如前所述 [2]，与市场有关的任何内容（例如，数字销售、拍卖、市场修改等）均已删除。 完整版本将包括 Syscoin 网络增强虚拟机 (NEVM)，它将利用以太坊虚拟机 (EVM) 与零知识证明 (ZKP) 系统相结合来构建可扩展的应用程序，并引入围绕以太坊燃料费的去中心化成本模型 （见表1）。

High gas fees and low transaction throughput are some of the key issues that are hindering ERC-20 projects from running at scale. Ethereum 2.0 is currently under development to address these issues. However, its final release is not anticipated to be completed for several years \cite{But19}. Instead of building a competing smart contract system, we have decided to work with the EVM protocol to build a faster, cost effective, alternative to Ethereum 2.0. To achieve this, the roadmap for Syscoin 4 proposes a four-layer tech-stack \cite{Sig21} comprised of: (a) Syscoin as the base layer to provide security; (b) EVM for programmability; (c) ZKP for scalability; and (d) applications to provide decentralized usability for the next phase of the internet's evolution, known as Web 3.0. 高燃料费和低交易吞吐量是阻碍ERC-20项目大规模运行的一部分关键因素。目前正在开发以太坊2.0以解决这些问题。但最终版本预计几年之内无法完成[4]。我们决定使用EVM协议来构建一个更快、更具成本效益的以太坊 2.0 替代方案，而非构建一个竞争性的智能合约系统。为实现这一目标，Syscoin 4 的路线图提出了一个四层技术堆栈 [1]，包括： (a) Syscoin 作为提供安全性的基础层； (b) 可编程性的 EVM； (c) ZKP 可扩展性； (d) 为互联网发展的下一阶段（称为 Web 3.0）提供去中心化可用性的应用程序。

In Section \ref{sec:protocol} we address the protocol attributes, which include Z-DAG, order-of-events, point-of-sale applications, assets, non-fungible tokens, Lightning Networks, offers/escrow, and masternodes. In Section \ref{section:roadmap} we lay out the roadmap for Syscoin 4, which includes scalability, design proposal, performance evidence, and applications. In Section \ref{section:specs} we outline the protocol specifications, and conclude the article in Section \ref{section:summary}. 章节II中讨论协议属性，包括Z-DAG、事件顺序、销售点应用程序、资产、不可替代的代币、闪电网络、商品/托管和主节点。 章节III中为 Syscoin 4 规划了路线图，其中包括可扩展性、设计提案、性能证据和应用程序。章节IV中概述了协议规范，章节V总结全文。

\begin{table}[h!]
\caption{Syscoin 4 Upgrades and Modifications Syscoin 4更新和修改}
\label{table:ugrades}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{|p{135pt}|p{75pt}|}
\hline
Syscoin功能 & 更新\\

\hline
即Z-Dag & 无更改\\
资产 &  修改\\

商品和去中心化市场 &   \\
~~~~~ 数字销售 &  已删除 \\
~~~~~ 拍卖 &  已删除 \\
~~~~~ 转售白名单 &  已删除 \\
~~~~~ 反馈和评分  &  已删除 \\
~~~~~ 多种付款方式 &  已删除 \\
~~~~~ 发货通知系统 &  已删除 \\
~~~~~ 市场审核 &  已删除 \\

数据锚定  &  已删除 \\
即时加密消息 &  更改用途 \\
区块链修剪 &  已删除 \\
证书（见身份） &  修改 \\
去中心化身份 &  新功能 \\
~~~~~ 证书 &  修改 \\
闪电网络 &  新功能 \\
商品/托管 &  修改 \\
Web 3.0 路线图  & \\
~~~~~ 网络EVM (NEVM)  &  新功能  \\
~~~~~ 零知识证明 &  新功能 \\
~~~~~ NEVM应用 &  提议 \\

\hline
\multicolumn{2}{p{251pt}}{已删除   $\rightarrow$ 从 Syscoin 4 中移除; 修改  $\rightarrow$ 升级自 Syscoin 3; 新功能  $\rightarrow$ 更新自Syscoin 3; 无更新 $\rightarrow$ 援引自Syscoin 3. }\\

@@

\section{Protocol Characteristics 协议特点}
\label{sec:protocol}

\subsection{Z-DAG}
Zero-Confirmation Directed Acyclic Graph (Z-DAG) is an instant settlement protocol functioning across all Syscoin services. Syscoin services consist of Alias Identities, Certificates, Escrow, Offers and Assets. Each service is controlled via an Alias, in which ownership is proven through a private key that matches each
unique address. Z-DAG organizes transactions based on dependencies to build the state in a deterministic fashion. This helps protect against double-spends where an asset is transferred falsely by creating multiple transactions through multiple nodes within a short time \cite{Sida18}. Z-DAG（零确认有向非循环图）是一种适用于所有Syscoin服务的即时结算协议。Syscoin服务包含别名身份、证书、托管、商品和资产。每项服务均由别名控制，并利用每个唯一地址所匹配的私钥来验证别名中的所有权。Z-DAG基于依赖关系，以决定性的方式构建状态，组织交易。这可以避免由于短时间内通过多个节点创建多个交易而错误地传输资产所造成的重复支付[2]。

\begin{figure}[h!]
\centering
\includegraphics[width=3in]{img/current_vs_zdag.png}
\caption{Current Blockchain design vs Z-DAG 当前的区块链设计vs Z-DAG} 
\label{fig:current_vs_zdag}
\end{figure}

Figure \ref{fig:current_vs_zdag}  shows the difference between a regular blockchain and Syscoin’s Z-DAG implementation. Syscoin now has two consensus layers. The upper layer consists of a Z-DAG graph of transactions are represented in the mempool without a block, providing settlement in real-time. The lower layer provides confirmation and conflict resolution preventing double-spend events through existing Proof-of-Work (PoW) consensus. 图1展示了常规区块链和Syscoin的Z-DAG之间的区别。目前，Syscoin有两个共识层：第一层中，在不含区块的内存池（mempool）中展示交易的Z-DAG图，提供实时结算。第二层通过现有的工作量证明共识进行确认并提供冲突解决方案，以防止双重支出问题。

When verifying, client nodes will create a graph of transactions topologically arranged via ascendants and descendants organized by the asset UTXO being spent. This is the most efficient approach as a circuit detection is not required; rather, it is inherently assumed as it is added to coin indexes in the memory pool. 验证时，客户端节点将创建一个交易图，通过已花费的资产UTXO 规划的先后，对这些交易进行拓扑排列。这是最有效的途径，因为无需电路检测；更确切的说，当它被添加到内存池中的硬币索引时，本质上也仅仅是假设。

Z-DAG is a transactional algorithm and does not affect consensus policy. It is meant to be a double-spend detection and prevention algorithm through the transaction policies of Syscoin Core. Z-DAG 是一种交易算法，不影响共识策略，目的在于通过 Syscoin Core的交易策略成为一种双重支出检测和预防算法。

A User Interface (UI) layer will notify the user of conflicts in real-time, allowing the transaction to occur in 3 to 5 seconds (i.e., the amount of time the network takes to notice that 2 double-spend transactions are conflicting with each other). This is possible through Syscoin’s Masternode layer that consists of incentivized full nodes paid an allocation of subsidy every block. Every masternode is connected to 25 or more peers, which facilitates high-throughput relay across the network, averaging one or more network hops to transmit from the sender to the receiver nodes. A 用户界面 (UI) 层将实时通知用户冲突，允许交易在3 -5秒之间发生（即网络注意到2个双重支出交易彼此冲突的时间）。这可以通过Syscoin的主节点奖励计划（Masternode）层实现，该层由激励的全节点组成，每个区块都支付补贴。每个Masternode连接到25个或更多的点，这些点在网络中提供高吞吐量的转播，将一个或多个网络跳数均衡从发送方传输到接收方节点。

To accurately detect double-spends, other implementations such as Phantom \cite{Som18} or Spectre \cite{Som15} must replace the longest chain rule to derive the order of events and attacker sequences in a graph.
These implementations end up in a more complex game theoretical situation that has not  been proven mathematically to be accurate in all cases. Syscoin relies on the thoroughly tested Nakamoto consensus model to arrive at a consensus over time rather than simply relying on a DAG. 为精准地检测出双重支出，其他的实施方案如Phantom [6] or Spectre [5]必须替换最长链规则，以推算出图表中事件和攻击者的顺序。最终这些实施方案会形成一个更复杂的、尚未从数学上证明所有情形都正确的博弈论。Syscoin并非仅仅依赖于一个DAG，而是凭借已全面测试的Nakamoto共识模型，以期逐渐达成共识。

\subsection{Order-of-events preservation and Conflict Resolution 事件保存及冲突解决的顺序}
Since assets have been migrated to a UTXO model in Syscoin 4, order-of-events and conflict resolution is as simple as relying on the existing UTXO policy of the Bitcoin memory pool code, which orders individual UTXO dependencies as ascendants and descendants per output. The conflict resolution code for double-spending an output was slightly adjusted from the Bitcoin policy by allowing one double-spend attempt for each output to propagate across the network. This ensures that a double-spend will always be detectable by an observer regardless of order-of-events. This is especially important as nodes on the network have no ability to understand the intent of a transaction and are thus not able to know which one is actually a double-spend attempt. To account for the extra bandwidth requirements of allowing a double-spend to be propagated, the minimum relay fee paid in the transaction is double that of a regular transaction. 由于资产已迁移到 Syscoin 4 中的 UTXO 模型，事件顺序和冲突解决就像依赖比特币内存池代码的现有 UTXO 策略一样简单，该策略将单个 UTXO 依赖项排序为每个输出的祖先和子孙。 通过允许对每个输出进行一次在整个网络中传播的双重支付尝试，从比特币政策中对双重支付的冲突解决代码进行微调。这确保了不管事件顺序如何，观察者始终可以检测到双重支付。 这一点尤其重要，因为网络上的节点无法理解交易的意图，因而也无法弄清究竟哪个才是双重支付尝试。考虑到允许传播双重支付需要额外带宽，交易中所需支付的最低中继费用是常规交易的两倍。

\subsection{CAP Theorem 定理}
The CAP theorem \cite{Bre12} states that it is impossible for a distributed data store to simultaneously provide more than two out of the following three guarantees: consistency, availability or partition tolerance. Bitcoin attempts to provide a guarantee that transactions are settled, but is not able to do so according to theory. Z-DAG partially trades consistency for availability. Since it is unlikely that a double-spend or re-organization will change the state of someone’s balance, we do not wait for settlement finality by waiting for blocks to confirm. This drastically increases the usability in point-of-sale applications. CAP定理[8]指出，分布式数据存储不可能同时提供如下三种保证中的两种以上：一致性、可用性或分区容错性。比特币试图提供一个交易已结算的凭证，但从理论上来看这是无法完成的。Z-DAG用可用性交换一致性。由于双重支出或重组不会改变人们的余额，我们无需等区块确认最终结算。这就极大地增加了POS应用程序的可用性。

The allowance of instant settlements and increased availability requires paying additional attention to users simply trying to double-spend or send transactions too quickly, which may cause the miner view to change from the general network view. The DAG will order the dependency graph of transactions and process in sequence, allowing for better availability (i.e., client making a request for data gets a response) when it comes to instant state changes. The same CAP constraints as PoW will provide a more responsive money transfer mechanism that may be used as a transaction processor instead of simply a settlement layer. 允许即时结算、提高可用性需要对一些用户进行额外的关注，因为这些用户仅仅只是尝试双重支出或发送交易过快，可能会导致矿工视图从一般网络视图改变。DAG将按序排列交易和进程的依赖关系图，以便在即时状态变化时达到更好的可用性（即，客户端请求数据得到响应）。CAP约束与工作量证明（PoW）相同，将提供一个更具响应性的资金转账机制，该机制可用作交易处理器，而非仅仅是一个清算层。

\subsection{Point-of-sale applications POS应用程序}
The combination of using assets with Z-DAG will allow for point-of-sale applications, providing real-time exchange of cryptocurrency assets/tokens. 资产和Z-DAG的组合将允许使用POS应用程序，为加密货币资产/代币提供实时交换

\subsection{Assets 资产}
We have created a coloured-coin implementation of a UTXO asset model where the commitment to the specific values of the assets are embedded in OPRETURN data carrying payload. The UTXO itself is part of the transaction to keep compatibility with the Bitcoin transaction format. The consensus to prove validity of an asset transaction is to simply compare the map of inputs (pairing of asset GUID and total value across all inputs) and the map of all outputs (pairing of asset GUID and total value across all outputs), which must be equal (note: there is no fee on assets so equality is sufficient to ensure validity). The coin database storing the unspent outputs adds a value to represent the asset identifier (GUID) for asset outputs. 我们创建了一个 UTXO 资产模型的彩色币执行器，对资产特定价值的承诺嵌入在携带有效载荷的 OPRETURN 数据中。 UTXO本身是交易的一部分，以保持与比特币交易格式的兼容性。达成证明资产交易有效性的共识，仅需比较输入映射（资产 GUID 和所有输入的总价值的配对）和所有输出的映射（资产GUID 和所有输出的总价值的配对），尤其应确保平等性（注意：资产不收费，因此平等性足以确保有效性）。在用以存储未花费输出的硬币数据库添加一个数值，来表示资产输出的资产标识符 (GUID)。

\subsection{Non-Fungible Tokens 非同质化代币}

Non-Fungible Tokens (NFTs) are unique Syscoin-based digital assets.  Some potential use cases include: gaming, digital art, physical assets, and digital collectibles. The advantages of using Syscoin over other platforms include, but is not limited to scalability, divisibility, efficiency, and notary capabilities. 非同质化代币(NFT) 是独一无二基于Syscoin的数字资产。一些潜在的实际用例如：游戏、数字艺术、实物资产和数字收藏品。与其他平台相比，使用 Syscoin 的优势包括但不限于可扩展性、可分割性、效率和公证能力。

By utilizing the NEVM, Syscoin will offer NFTs running on the application layer of its tech-stack, which will offer a competitive advantage over Ethereum in terms of scalability. Another interesting feature Syscoin will offer is divisibility. A good example of this is land ownership where fractions of such assets can be apportioned between multiple parties. Finally, developers will be able to employ notary capabilities by applying custom rule sets to transactions involving NFTs. 通过应用NEVM，Syscoin 将提供在其技术堆栈的应用层上运行的NFT，NFT在可扩展性方面竞争优势优于以太坊。 Syscoin提供的另一个有趣的功能是可分割性。土地所有权就是一个很好的例子，这种资产的一部分可以在多方之间分配。 最后，通过将自定义规则集应用于涉及 NFT 的交易，开发者将能够使用公证功能。

NFT, fractional or otherwise, are implemented in the UTXO asset model and of course can be deployed using the ERC-related specifications on the NEVM model as is the case with Ethereum. Notary capabilities are only implemented for the UTXO asset model. However, with validity proofs we are looking to integrate such features on the NEVM model as well. NFT以一部分的形式或以其他方式在 UTXO 资产模型中实现，当然可以像以太坊一样使用NEVM模型上的ERC相关规范进行部署。公证能力仅适用于 UTXO 资产模型。 通过有效性证明，我们希望在 NEVM 模型上也可以集成这些功能。
